---
title: "P&A hand priming demo analysis"
author: "Cordula Vesper"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(signal)
#Make sure you're in the folder where your data is
getwd()
setwd("/Users/FlowersnIce-cream/Google Drev/Hogwarts/4/Models for perception and action/Exam/3 - Movements/W13 - Motion tracking and analysis/Exp/")

```

Part 1. Remind yourselves what we did in the study and what we expected and why.

Simple implementation of a hand-priming-effect with 4 conditions (distractors/target): 1) high/low; 2) low/low; 3) high/high; 4) low/high
#8 søjler - Først fem har samme højde, så en lavere, så store igen. - Primet til at hoppe højere når den lave søjle kommer.
#Der skete ikke noget hvis man ramte søjlerne (Selvom folk nok stadigt troede det) ->


Part 2. Load one trial of your choice into R. The four columns refer to: sample, condition, x and y.

```{r}
participant <- 21
trial <- 12
filename <- paste(participant,'/',participant,'_',trial,'.txt',sep="")
hp = read.table(filename,header=FALSE,sep=",",dec=".")
names(hp) <- c("sample","cond","x","y") 
```

Part 3. Plot x against y.

```{r}
plot(hp$x,hp$y,'l')
```

Part 4. Map the y data to a more intuitive screen output with 0/0 in the lower left corner and where upwards movements are increasingly positive (i.e. so that it looks like the movements we made on the screen). 

This was unnecessary, sorry!


Part 5. Calculate the distance travelled (for x and y combined). -> The Whole Path (Don't worry about it - No Pythagora)
# diff har som default lag1, which means that it takes the previous value and calculates the difference
#powered and squared to avoid minus.
```{r}
dist <- sum(sqrt(diff(hp$x)^2 + diff(hp$y)^2)) 
paste("Distance: ",round(dist))
```

Part 6. Add a time vector. I forgot to measure time so I had to estimate it post-hoc (fine for this exercise, not great if it was a real experiment). We can assume that each sample takes .0025 s.
# All rows minus 1 - in the first row, time should be 0
```{r}
hp$t <-  (hp$sample-1) * 0.0025
```

Part 7. Calculate velocity and acceleration for y, i.e. vertical movement (Up and down). Remember: Velocity = distance difference / time difference. Acceleration = velocity difference / time difference.

```{r}
hp$vel <- c(0,diff(hp$y) / diff(hp$t))
hp$acc <- c(0,diff(hp$vel) / diff(hp$t))
plot(hp$t,hp$acc,'l')
lines(hp$t,hp$vel,'l')
lines(hp$t,hp$y,'l')
#max(hp$y)
#max(hp$vel)
#Wierd to have all on the y axis
title("position, velocity, acceleration")
```

Part 8. Play around with some filter to smoothen velocity and acceleration (most common: Butterworth filter).

```{r}
?butter()
"""
#n	
filter order or generic filter model
#W	
critical frequencies of the filter. W must be a scalar for low-pass and high-pass filters, and W must be a two-element vector c(low, high) specifying the lower and upper bands. For digital filters, W must be between 0 and 1 where 1 is the Nyquist frequency.
-> Low Pass = Lower values can pass -> Make it more smooth
"""
# requires signal package
bf <- butter(2, 0.1, type ='low') 
hp$velf <- filtfilt(bf,hp$vel)
plot(hp$t,hp$vel,'l', col = "black")
lines(hp$t,hp$velf,'l', col = "red")
title(paste("velocity (filter cutoff ",0.1,")",sep=""))

bf <- butter(2, 0.01, type ='low')
velf_test <- filtfilt(bf,hp$vel)
plot(hp$t,hp$vel,'l', col = "black")
lines(hp$t,velf_test,'l', col = "red")
title(paste("velocity (filter cutoff ",0.01,")",sep=""))

bf <- butter(2, 0.1, type ='low')
hp$accf <- filtfilt(bf,hp$acc)
plot(hp$t,hp$acc,'l', col = "black")
lines(hp$t,hp$accf,'l', col = "red")
title(paste("acceleration (filter cutoff ",0.1,")",sep=""))
```

Part 9. Using zero crossings in the velocity, calculate y position extreme values (maxima and minima). Mark those extreme values on top of the x/y plot you made earlier.
```{r}
#Normally velocity can't go into minus, but in pixel movement you can -> So finding changes over 0, means peaks and valleys.

```

Part 10. Using e.g. a range of x positions, specify a segment during which the critical movement happens, i.e. the 6th movement is what we would want to compare in this study. Mark the peak in that segment in a different color.

```{r}
zcr <- c(0,diff(sign(hp$velf)))
zcrMin <- zcr==2
zcrMax <- zcr==-2
plot(hp$x,hp$y,'l')
points(hp$x[zcrMin],hp$y[zcrMin],col = "black")
points(hp$x[zcrMax],hp$y[zcrMax],col = "green")

zcrTarget <- hp$x>1160&hp$x<1330&zcrMax
paste("Target position (x) and value (y): ",hp$x[zcrTarget],hp$y[zcrTarget])
points(hp$x[zcrTarget],hp$y[zcrTarget],col = "red")
title(paste("participant",participant,"trial",trial,"condition",hp$cond[1]))
```



# EXTRA - Telma
```{r}
#Telma
data <- hp
data$velextreme <- ifelse(data$vel < 20 & data$vel > -20, 1,0)
# derivative of velocity is acceleration => the local maxima and minima are at those points where the derivative is 0
# center the data by substracting the minimum values
data$x_center <-  data$x - min(data$x)
data$y_center <-  data$y - min(data$y)

ggplot(data) +
  geom_point( aes(x_center,y_center, color = factor(velextreme), size = velextreme)) + 
  # plot by this factor, you get the zero crossing plotted in the different color
  labs(x = "Trajectory", y = "Height")

localmax <- max(data$y_center[2200:2400])
which(data$y_center == 267.336) # 2350
data$colorvel<- ifelse(data$y_center == localmax ,1,0)

ggplot(data) +
  geom_point( aes(x_center,y_center, size = colorvel, color = factor(colorvel))) + 
  #geom_point( aes(x_center,y_center, size = factor(velextreme))) +
  # plot by this factor, you get the zero crossing plotted in the different color
  labs(x = "Trajectory", y = "Height") +
  theme(legend.title = element_blank(), legend.position='none')

```

