---
title: "Visualizing semantic distance"
author: "Adam finnemann"
date: "November 9, 2017"
---
Read in ggplot2/tidyverse, set working directory and load the data from the semantic distance exercise.
```{r}
library(tidyverse) ; library(ggplot2)
setwd("/Users/FlowersnIce-cream/Google Drev/Hogwarts/R Studio/work/CLasswork/Adam Semanticmap - 8")
your_data <- read.csv("Harry Potter.csv")
```
Inspect the data frame and make sure you understand each of the columns.



Replace "your_data" with your data frame and plot the development of semantic distance over time.
```{r}

ggplot(your_data, aes(word_nr, distance, label = word,  color = distance)) + 
  geom_point() + 
  geom_line() +
  geom_text(check_overlap = T, position =  position_jitter(height = 2))+
  ggtitle("Lineplot of semantic distance (trial by trial)")
```
Interpret the plot:
What does small and large jumps on x-axis mean? 
Answer:

Does it seem like we search for words like we forage after food? 
Answer:




With your own data frame make a histogram as well. You can try different values of "binwidth" to see if you can find an interesting/pretty pattern.
```{r}
your_data %>% 
  filter(distance != 100) %>% 
  ggplot(aes(distance, color = distance)) +
  geom_histogram(binwidth = 5, aes(fill = ..count..)) +
  scale_fill_gradient("count", low="orange", high="purple") +
  labs(x = "Distance", 
       y = "Count", 
       title = "Semantic distance distribution") +
  scale_x_continuous(breaks = seq(0,100,5))


```
Interpret the plot: 
How is the semantic distance between words distributed?


Lastly, make a correlation analysis between time and distance. Make a scatterplot as well to help you interpet the correlation.
You did correlation analysis as well as scatter plots last time in the Russian Blue experiment analysis. You can reuse that code.
```{r}
ggplot(your_data, aes(x=time, y=distance, color=distance))+geom_point()+geom_smooth(method = "lm")
```

